MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-23 paper.Rmd
More on the paper.

The matrix approach to data storage brings the challenge that 
different countries, 
and different years for a given country,
have varying energy products and varying energy processing machines.

Given the decision to use PSUT matrices to store ECC data,
packages were created to enable manipulation of matrices
within the tidyverse, as shown in the following table.

| Package | Function |
|---------|----------|
| [RCLabels](https://matthewheun.github.io/RCLabels/)      | Manipulate row and column matrices |
| [matsbyname](https://matthewheun.github.io/matsbyname/)  | Perform matrix mathematics that respects row and column names |

It would be convenient to perform matrix mathematics in `R` data frames
as easily as scalar mathematics in data frames.

with the `dplyr` package from the `tidyverse`.
To do that, a way to embed matrices in a cell of a data frame is required.

Further, a means of manipulating row and column names

One problem is da

that

To solve these problems and 
to meet the need for the SEA community,
we developed a suite of `R` packages.

to enable 
analyses for all countries, as described in the following table.

>>>>

The matrix approach to data storage brings the challenge that 
different countries, 
and different years for a given country,
have varying energy energy carriers (products) and
varying energy conversion machines (industries).
To get around this challenge, a new `R` package 
[matsbyname](https://matthewheun.github.io/matsbyname/)
enables matrix mathematics that respects row and column names, 
inserting `0` rows or columns where needed.

Furthermore, 
it would be convenient to perform matrix mathematics in `R` data frames
as easily as scalar mathematics in data frames with [tidyverse](https://www.tidyverse.org) syntax. 
[matsindf](https://matthewheun.github.io/matsindf/) enables this functionality.

| Package | Function |
|:--------|:---------|
| [RCLabels](https://matthewheun.github.io/RCLabels/)      | Manipulate row and column names in [matsindf](https://matthewheun.github.io/matsindf/) data frames |
| [matsbyname](https://matthewheun.github.io/matsbyname/)  | Perform matrix mathematics that respects row and column names |
| [matsindf](https://matthewheun.github.io/matsindf/)      | Store matrices in cells of a data frame, thereby enabling [tidyverse](https://www.tidyverse.org) syntax |

The packages in the table above are applicable to many problem domains and
are available on [CRAN](https://cran.r-project.org).

Additional packages specific to ECC analysis within SEA are available on GitHub
and described in the following table.

| Package | Function |
|:--------|:---------|
| [Recca](https://matthewheun.github.io/Recca/) | Functions to perform `R` energy conversion chain analysis |
